PhD Title \\ PhD Thesis

### 2024-08-02 Latex_files/Thesis/chapters/chapter 2/main.tex
tidying up chapter 3

@@

Throughout this PhD we use the work of Vigilante to perform a systematic 
study of the dynamics demonstrated by asymmetric dimers in both plane and 
circularly polarised light. But furthermore we expand upon their work to 
create a fully functional quadrant photo-diode to simulate the response 
from a calibration test. This builds upon the work from \cite{Rohrbach2002} 
which applied the fundamental principles of Lorenz-Mie theory to replicate 
the response signal of a QPD being used in back focal-plane interferometry.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Quadrant Photodiode}
\label{sec:simulated_QPD}
In order to simulate a typical experimental set up with a QPD installed 
as a position detection system we need to evaluate the total magnitude of 
the electric field incident on the photo-diode surface. While trapping a 
micro-particle, the scattered and incident fields combine together and 
interfere with one another. These fields are collected by a condenser 
lens in the far field limit and are focused onto the QPD surface, the 
total intensity can be evaluated as:
\begin{align}
I(x,y) = \epsilon_0c\left|
\begin{bmatrix} 
	E_{i,x}(x,y)+E_{s,x}(x,y) \\ 
	E_{i,y}(x,y)+E_{s,y}(x,y) \\ 
	E_{i,z}(x,y)+E_{s,z}(x,y)
\end{bmatrix} \right|^2 \times step(NA_c-\sqrt{x^2+y^2})
\end{align}

>>>>

\subsubsection{Power spectral analysis for rotating objects}
The scattering from rotating objects can be partially characterised via
the power spectrum density method. Typically papers reporting on the 
rotation rate of a trapped object will collect a power spectrum and look
at the maximum frequency term to determine its rotation rate. However this
often neglects any information on the trapping forces acting on particle
and only looks at the torque applying around one of the particle's primary 
axis. There has only been one notable effort to fully characterise the 
full trapping dynamics on a rotating body, \cite{Yogesha2012} developed 
a theoretical model for that relates the power spectrum to both the 
rotational and translational motion simultaneously.

@@

\subsection{Simulation parameters}
Throughout this PhD we use the work of Vigilante to perform a systematic 
study of the dynamics demonstrated by asymmetric dimers in both plane and 
circularly polarised light. The simulations have two primary frames of 
reference that require explanation. Firstly, there is the laboratory frame 
which describes the coordinate system, we define the origin of our simulation
as the focus of our trapping beam. While the choice in direction for the $x$ 
and $y$ axis are arbitrary the $z$ axis is specifically chosen so that it is 
aligned with the direction of beam propagation. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.6\linewidth]{lab_frame.png}
	\caption{Ray scattering render of both the laboratory frame and particle 
		frame for a dimer and a Gaussian beam. The origin of the laboratory 
		frame is defined as the focus of the trapping beam, with the positive 
		$z$-axis being aligned with the direction of beam propagation. The 
		particle frame is centered on the dimer's centre of mass with the 
		primary axis $U_z$ being aligned with the centres of the two spheres.
		Black line is scaled to represent $1\ \mu m$.}
	\label{fig:lab_frame} 
\end{figure}

Secondly there is the particle frame which describes the orientation state of 
the particle, orientations are reported as quaternions which can be readily 
transformed into rotation matrices. The matrix describes the direction of the 
particles 3 orientation axis $U_x$, $U_y$, and $U_z$; the latter is oriented 
so that it is collinear with the centres of the two spheres. The origin of 
the 3 axis' is set on the particle's centre of mass, this is also used to 
define it's displacement from the origin of the laboratory frame.

Furthermore we expand upon their work to create a fully functional quadrant 
photo-diode to simulate the response from a calibration test. This builds 
upon the work from \cite{Rohrbach2002} which applied the fundamental 
principles of Lorenz-Mie theory to replicate the response signal of a QPD 
being used in back focal-plane interferometry.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulated Quadrant Photodiode}
\label{sec:simulated_QPD}
In order to simulate a typical experimental set up with a QPD installed 
as a position detection system we need to evaluate the total magnitude of 
the electric field incident on the photo-diode surface. While trapping a 
micro-particle, the scattered and incident fields combine together and 
interfere with one another. These fields are collected by a condenser 
lens in the far field limit and are focused onto the QPD surface, the 
total intensity can be evaluated as:
\begin{align}
I(x,y) = \epsilon_0c\left|
\begin{bmatrix} 
	E_{i,x}(x,y)+E_{s,x}(x,y) \\ 
	E_{i,y}(x,y)+E_{s,y}(x,y) \\ 
	E_{i,z}(x,y)+E_{s,z}(x,y)
\end{bmatrix} \right|^2 \times step(NA_c-\sqrt{x^2+y^2})
\end{align}
